Methods for Large Scale Learning to Rank

### 2014-04-10 report/Chapters/CrossBenchmarkComparison.tex
cross-comparison
cross-metric comparison

The cross-metric comparison is based on the \ac{nDCG}@3, \ac{nDCG}@5, \ac{nDCG}@10 and \ac{MAP} comparisons combined, which justifies analysing the comparison more thoroughly. Figure \ref{fig:normalised_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size.

>>>>

The cross-metric comparison is based on the \ac{nDCG}@3, \ac{nDCG}@5, \ac{nDCG}@10 and \ac{MAP} comparisons combined, which justifies analysing the comparison more thoroughly. Figure \ref{fig:normalised_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

LRUF, FSMRank, FenchelRank, SmoothRank and ListNet showed to be the methods that have no other method superior to them in both Ideal Winning Number and Normalised Winning Number. LRUF is the only methof that achieved this in all \ac{nDCG} comparisons, the \ac{MAP} comparison as well as the cross-metric comparison. With FenchelRank, FSMRank, SmoothRank and ListNet being among the top performing methods in all \ac{nDCG} comparisons as well as in the cross-metric comparison, it can be concluded that the cross-metric results are highly defined by the \ac{nDCG} performance as opposed to the \ac{MAP} performance. This was to be expected, because the cross-metric comparison input data of three \ac{nDCG} entries (@3, @5, and @10) enables it to have up to three times as many as many weight as the \ac{MAP} comparison.
